Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-27 paper/paper.discussion.tex
Work on discussion

Our formulation includes hard constraints to ensure the schedule satisfies hospital and logistics requirements. It also aims to satisfy the work preferences of clinicians in a clinical department by optimizing a multi-goal objective function [...] \\

>>>>

Our formulation includes hard constraints to ensure the schedule satisfies hospital and logistics requirements. It also aims to satisfy the work preferences of clinicians in a clinical department by optimizing a multi-goal objective function. While one of our goals was to keep a minimal set of constraints to ensure that the ILP formulation is usable in practice, it leaves room to adapt it to various clinical departments at different hospitals. The flexibility of our ILP allows changing the number of services provided in a division, the length of a work block, clinicians' preference for work block to weekend adjacency as well as clinicians' requests for time off. \\
